%===============================================================================
\section{Project Progress Summary}

% !!! Reference back to the project plan !!!

% Provides a concise and informative summary of what has been achieved so far.
% Provide a high-level overview of the project's current status. Briefly mention problematic or delayed work packages, issues, or blockers that require stakeholder attention.


% TEAM LEADER will write this section!! No one is allowed to write here. 


% Overview of work package status 
The project has seen significant progress since it was launched. As of \today,\: 3 out of 14 work packages have been completed, 8 are in progress, 1 has not started yet (upcoming), 2 is on hold and 0 have been cancelled. Note that this does not include the two \ac{hil} work packages which are outside of both the current and the next work period.
% Issues
The projects main threat is time, the project might be able to deliver the individual parts, but the integration of all the parts into a complete functioning package is unrealistic. Additionally, to keep within the limited timeline and budget, optimal and tailor-made solutions had to be sacrificed in favour of simpler ones. This in turn makes it improbable for the final product to function according to the initial demands placed by the stakeholders (capable of competing).
% Stakeholder attention
% Software
The software side of the project is progressing well except for 1.5.5 \textit{nav2 stack configuration} which has proven especially problematic, this still remains to be solved. This has in turn resulted in 1.5.6 \textit{Develop supporting functions} being placed on hold.
% Hardware
The hardware development is progressing but not at the necessary speed to deliver the product by December. Problems with 2.2.1 \textit{Manufacture \acs{pcb}} and the fact that the components have yet to arrive has caused noticeable issues for the hardware team.
See Table.\:\ref{tab:activity_status} for a complete overview of the project status.

%-------------------------------------------------------------------------------

\begin{comment}
Work packages that have been completed are: 
Work packages that are in progress are: 
Work packages that are not started yet are: 

The main issues we had so far are................These issues have caused \textbf{(Delay, blocking or risk of ON track work packages)}
The issues are (solved, still have them) and we plan to solve them by...... 
\end{comment}

%===============================================================================